---
title: "MPG Warehouse Index"
output:
  flexdashboard::flex_dashboard: 
    theme: spacelab
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
```

Sidebar {.sidebar data-width=250}
=====================================
```{r}
selectInput("subject",
            "Data subject:",
            choices = c("Weather", "Vegetation", "Biomass", "Point Count",
                        "Bird"),
            selected = c("Weather"),
            multiple = TRUE)
```

Application
=====================================

Column {.tabset data-width=750}
-----------------
* [Ranch Weather](https://mpg-data.shinyapps.io/weather/){target="_blank"}
* [Data Warehouse Index](https://mpg-data.shinyapps.io/warehouse_index/){target="_blank"}
* [Surveys](https://mpg-data.shinyapps.io/mpg_surveys/){target="_blank"}

Documentation
=====================================

Column {.tabset data-width=750}
-----------------
* [Readme vegetation point-intercept cover survey](https://docs.google.com/document/d/1JWnhxNjeSQZkSnGhtHP68i_l1mDj4vPFMBdUvGqN0TA/edit?usp=drivesdk target="_blank")
* [Readme vegetation line-quadrat cover survey](https://docs.google.com/document/d/16-Aq8u9Rudd78fSzfjvpCXyQgE-BstC-d2PjYfmLtcw/edit?usp=drivesdk target="_blank")
* [Readme Weather Data](https://docs.google.com/document/d/1WKzE0v4DiwlfKYjMvTEVgzp_-_6jAv4l4CAtqqy-aII/edit?usp=drivesdk target="_blank")
* [Readme bird point count monitoring](https://docs.google.com/document/d/1PRryJzGOUtfr-fKXzb3tbr48xiaTuAMVk18XFXlvxcM/edit?usp=drivesdk target="_blank")
* [Readme vegetation species metadata](https://docs.google.com/document/d/1aRGYGPsuHmuOxi29bfdzaackjJkfCEY3T2Z3rekQUbY/edit?usp=drivesdk target="_blank")
* [Readme grid point metadata](https://docs.google.com/document/d/1dQf3WIp2JaOTFKFo8eOj-J6tFByUA22cu_VyTbeGPa8/edit?usp=drivesdk target="_blank")
* [Readme Property Information](https://docs.google.com/document/d/1aQIMIW3Fkic7VN8dr4SgkIIVblM9TkD3Kog8zkTU7q4/edit?usp=drivesdk target="_blank")
* [Readme vegetation biomass](https://docs.google.com/document/d/1AF8qh7YRqEJ_5DjX0GrA3Z52RfGp2f22Jc2uLonGa2I/edit?usp=drivesdk target="_blank")
* [Readme vegetation survey methods critique](https://docs.google.com/document/d/1I5pqZoqV0CJ5452uxkD5JR-RvsLb4qBWSa8O6dyMams/edit?usp=drivesdk target="_blank")
* [Readme Soil Moisture](https://docs.google.com/document/d/1uZ8al-Zhtm3G3Eeaik-5QHnxgfdyHuHXrLJwfMQXUXY/edit?usp=drivesdk target="_blank")
* [Readme plant phenology data](https://docs.google.com/document/d/1D5OAvutLfdV5_9DstpWbi72aVxlksCF_QVLOtf9vWh8/edit?usp=drivesdk target="_blank")
